cardinalR: Generating Interesting High-Dimensional Data Structures

### 2025-12-17 paper-cardinalR.Rmd
Updated Figure 7

proj_obj1 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -1.1, 
                                              axis_pos_y = -1.1, 
                                              threshold = 0.1))

@@

proj_obj2 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 2,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -2.2, 
                                              axis_pos_y = -2.2, 
                                              threshold = 0.18))

@@

proj_obj3 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 1.4, 
                                              axis_pos_x = -1.2, 
                                              axis_pos_y = -1.2, 
                                              threshold = 0.1))

@@

proj_obj1 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -0.5, 
                                              axis_pos_y = -0.5, 
                                              threshold = 0.022))

@@

proj_obj2 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -0.65, 
                                              axis_pos_y = -0.65, 
                                              threshold = 0.06))

@@

proj_obj1 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 2.5,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -2, 
                                              axis_pos_y = -2, 
                                              threshold = 0.2))

@@

proj_obj2 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 2,
                                              axis_scaled = 1, 
                                              axis_pos_x = -2.9, 
                                              axis_pos_y = -2.9, 
                                              threshold = 0.1))

conicspiral_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-3.3, 2), 
  title = "c2", 
  cex = 2, 
  axis_text_size = 4,
  is_color = FALSE)

@@

proj_obj3 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 2.5,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -2.3, 
                                              axis_pos_y = -2.3, 
                                              threshold = 0.2))

@@

proj_obj1 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -0.3, 
                                              axis_pos_y = -0.3, 
                                              threshold = 0.1))

@@

proj_obj2 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 1.3, 
                                              axis_pos_x = -0.5, 
                                              axis_pos_y = -0.5, 
                                              threshold = 0.1))

nonlinear_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 2), 
  title = "d2", 
  cex = 2, 
  axis_text_size = 4,
  is_color = FALSE)

@@

>>>>

proj_obj1 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1.4,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -1, 
                                              axis_pos_y = -1, 
                                              threshold = 0.1))

@@

proj_obj2 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 2.6,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -2.1, 
                                              axis_pos_y = -2.1, 
                                              threshold = 0.18))

@@

proj_obj3 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1.4,
                                              axis_scaled = 1.4, 
                                              axis_pos_x = -1.1, 
                                              axis_pos_y = -1.1, 
                                              threshold = 0.1))

@@

proj_obj1 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.9,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -0.5, 
                                              axis_pos_y = -0.5, 
                                              threshold = 0.09))

@@

proj_obj2 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -0.63, 
                                              axis_pos_y = -0.63, 
                                              threshold = 0.06))

@@

proj_obj1 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 3.4,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -1.8, 
                                              axis_pos_y = -1.8, 
                                              threshold = 0.2))

@@

proj_obj2 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 3,
                                              axis_scaled = 1, 
                                              axis_pos_x = -3.1, 
                                              axis_pos_y = -3.1, 
                                              threshold = 0.2))

conicspiral_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-3.6, 2), 
  title = "c2", 
  cex = 2, 
  axis_text_size = 4,
  is_color = FALSE)

@@

proj_obj3 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 3.4,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -2.2, 
                                              axis_pos_y = -2.2, 
                                              threshold = 0.2))

@@

proj_obj1 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1.2,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -0.3, 
                                              axis_pos_y = -0.3, 
                                              threshold = 0.1))

@@

proj_obj2 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1.8,
                                              axis_scaled = 1.3, 
                                              axis_pos_x = -0.6, 
                                              axis_pos_y = -0.6, 
                                              threshold = 0.18))

nonlinear_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.9, 2), 
  title = "d2", 
  cex = 2, 
  axis_text_size = 4,
  is_color = FALSE)

@@

proj_obj3 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.9,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.43, 
                                              axis_pos_y = -0.43, 
                                              threshold = 0.07))
